A significance test in forward stepwise regression

### 2014-04-03 paper/paper.tex
rough cut and paste of quadratic materila

@@

Forward stepwise regression is a classical model selection procedure
that begins with an empty model and sequentially adds the best predictor
variable in each step. The usual $\chi^2$ and $F$-tests for significance
fail when a model has been selected this way and tend to be
anti-conservative unless they are computed on a held-out validation
dataset. In the lasso setting, \cite{significance:lasso} derived
a novel test statistic and its asymptotic null distribution, making
possible valid inferences after model selection using the full data.
\cite{tests:adaptive} modified and extended those results to the
group lasso \citep{grouplasso} and other penalized regression
problems, but only under the global null hypothesis.
One of the strengths of these test statistics is that they can be
used for valid significance testing when computed on the same
data used for model selection, eliminating the need for data splitting.
The present work iteratively applies the global null test
of \cite{tests:adaptive} for each step in forward stepwise selection,
and works out some of the details necessary for
models with grouped variables. The resulting method can
be more statistically efficient than validation on held-out data, and
more computationally efficient than penalized methods with
regularization parameters chosen by cross-validation.

In Section~\ref{sec:stepwise} we establish notation and describe the
forward stepwise algorithm used in most of the paper.
Section~\ref{sec:testing} briefly reviews
the parts of \cite{significance:lasso} and \cite{tests:adaptive}
relevant to our significance test, and describes the group lasso which
we require for applying the test with grouped variables.
Simulation results in Section~\ref{sec:simulations} show
empirically that our method performs well in settings where forward
stepwise itself performs well, and that
various stopping rules using our test statistic--including
some from \cite{sequential:fdr}--appear promising. In
Section~\ref{sec:applications} we apply
the method to several variants of forward
stepwise tailored to models with interactions and generalized additive
models, as well as to a real data example.
(\todo Change this paragraph if necessary as the sections are completed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Denote $y \in \real^n$ for $n$ i.i.d. measurements of the outcome variable.
Let an integer $G \geq 2$ be the number of groups of explanatory variables.
For each $1 \leq g \leq G$ the design matrix encoding the
$g$th group is the $n \times p_g$ matrix denoted $X_g$, where $p_g$ is
the number of individual variables or columns in group $g$.
% Do we need to assume $p_g \ll n$ or $\text{rank}(X_g) = p_g$?
When a group encodes a categorical variable as binary indicators for the
levels of that variable, we use the full encoding with a column for every
level. Although this introduces collinearity, our method does not require
the design matrix to have full rank.

Define $p = \sum_{g=1}^Gp_g$,
the total number of individual variables, so $p = G$ in the
case where all groups have size 1. Let $X$ be the matrix constructed
by column-binding the $X_g$, that is  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{equation*}
X = \begin{pmatrix} X_1 & X_2 & \cdots & X_G  \end{pmatrix}
\end{equation*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We assume throughout that the individual columns of $X$ are scaled to
have unit 2-norm (we do not scale groups, this is accomplished later
by weighting).
With each group we associate the $p_g \times 1$ coefficient vector
$\beta_g$, and write $\beta$ for the $p \times 1$ vector constructed
by stacking all of the $\beta_g$ in order.  Finally, our model for the
response is
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{equation}
\begin{aligned}
\label{eq:gmodel}
y & = X \beta + \sigma \epsilon \\
   & = \sum_{g=1}^G X_g \beta_g + \sigma \epsilon
\end{aligned}
\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
where $\epsilon$ is noise. We assume Gaussian noise
$\epsilon \sim N(0, \Sigma)$ with known covariance matrix $\Sigma$.

@@

\begin{algorithm}
  \caption{Forward stepwise variant with groups and weights}
  \label{algo:fs}
  \begin{algorithmic}[1]
    \REQUIRE An $n$ vector $y$ and $n \times p$ matrix $X$ of $G$ variable groups with weights $w_g$
    \ENSURE Ordered active set $A$ of variable groups included in the model at each step
    \STATE $A \gets \emptyset$, $A^c \gets \{ 1, \ldots, G\}$
    \FOR{$s=1$ to $steps$}
    \STATE $g^* \gets \argmax_{g \in A^c} \{ \norm{X_g^T r_{s-1}}_2 / w_g \}$
    \STATE $P_g \gets I_{n\times n} - X_{g^*}X_{g^*}^\dagger$
    \STATE $A \gets A \cup \{ g^* \}$, $A^c \gets A^c \backslash \{ g^* \}$
    \FORALL{$g \in A^c$}
      \STATE $X_g \gets P_g X_g$
    \ENDFOR
    \STATE $r_s \gets P_g r_{s-1}$
    \ENDFOR
    \RETURN $A$
  \end{algorithmic}
\end{algorithm}

The active set $A$ contains variable groups chosen to be included in
the model. Fitting $\hat \beta$ can be done by tracking the individual
fits and projections, or by simply fitting a linear model on the submatrix
of $X$ corresponding to $A$. 
We now use forward stepwise to refer specifically to
Algorithm~\ref{algo:fs} unless otherwise specified. Note that other
implementations of forward stepwise use different criteria for choosing
the next variable to add, such as the correlation with the residual.
Since we do not renormalize the columns after projecting the covariates
(lines 6 to 8 above), and since we have weights, we are not computing
correlations unless the design matrix is orthogonal and all weights are 1.
There are advantages and disadvantages to both criteria which we do not
discuss. Our choice was motivated by the group lasso result in
\cite{tests:adaptive}, but we believe other criteria can be handled
with appropriate modifications.

@@

Among model selection procedures, forward stepwise is one which performs
variable selection: from a potentially large set of variables it chooses
a subset to include in the model. The most general form of variable
selection is called subset selection, a procedure which searches among
all $2^G$ subsets of $G$ variable groups and picks the best model.
This exhaustive search is computationally infeasible when $G$ is
large, and when possible it still
runs the risk of over-fitting unless model complexity is
appropriately penalized (as in \eqref{eq:subsetregress} below).
Forward stepwise produces a much
smaller set of potential models, with cardinality at most
\textit{steps}. However
it is a greedy algorithm, so the set of models it produces may not
contain the best possible model. This is an inherent shortcoming of
forward stepwise procedures and should be kept in mind when choosing
between model selection methods.

@@

For various sparsity levels $k$, Algorithm~\ref{algo:fs} was run on
various data sets with \textit{steps} equal to $k$ and the ``average
power'' was calculated as the number of true variables in the active
set after $k$ steps divided by $k$. (\todo Make this consistent with
$\gamma$ in simulations section)
Nonzero coefficients had magnitude
in a range of multiples of $\gamma := \sqrt{2\log(G)}$, e.g. in $[1.4
\gamma, 1.6 \gamma]$. Results are shown in
Figure~\ref{fig:fwdstepsim}. After computing the
coherence of these design matrices, some calculations show the required
sparsity level to guarantee exact recovery in these situations is
about 2 or smaller, and the required nonzero coefficient magnitude is
likely in the range of 10 to 100 times $\gamma$. These simulations are far
from the stringent conditions required by theory to guarantee perfect
recovery, but the performance, while not perfect, may still be good
enough for some purposes.

@@

Writing $\hat \beta(\lambda)$ for the lasso solution for a fixed value of $\lambda$, we need
the following facts summarized in \cite{significance:lasso} (ref Tibs2012?).

@@

  \item The vector valued function $\hat \beta(\lambda)$ is a
    continuous function of $\lambda$. For the lasso path, the
    coordinates of $\hat \beta(\lambda)$ are piecewise linear with
    changes in slope occurring at a finite number of $\lambda$ values
    referred to as \emph{knots}. The knots depend on the data and are
    usually written in order $\lambda_1 \geq \lambda_2 \geq \cdots
    \geq \lambda_r \geq 0$. We follow this convention.

  \item The \emph{active set} $A_k$ is a set of indices of variables
    for which the corresponding coordinates of $\hat \beta(\lambda_k)$
    are potentially nonzero. Any variable with index not in $A_k$ has
    a zero coefficient in $\hat \beta(\lambda_k)$, but the converse is
    not true. \todo{is this equicorrelation set?}

  \item Path algorithms for computing lasso solutions proceed by
    fitting models at a grid of $\lambda$ values. The active set
    changes whenever $\lambda$ crosses a knot, and predictor variables
    can both enter and leave the active set. However, at the first two
    knots $\lambda_1$ and $\lambda_2$ no variable can leave the active
    set. So the first two knots correspond to the first two variables
    entering the model.

@@

\cite{significance:lasso} prove that under the null hypothesis that $A_k$
contains all the strong predictor variables, the distribution of a
test statistic $T_k \propto \lambda_k(\lambda_k - \lambda_{k+1})$ is
asymptotically Exp(1). In the lasso case we know a lot about the knots
and active set, but the group lasso picture is slightly more
complicated. For the group lasso, $\hat \beta(\lambda)$ does not have
piecewise linear components. To overcome this difficulty we
restrict our attention to the first group of variables to enter the
active set since the analysis then follows almost exactly as for the
lasso.

@@

@@

Before considering the group lasso, we review some ingredients of the
proof for the lasso. Let $J = \{ 1, 2, \ldots, p \}$ index variables
and consider a stochastic process $f_{j,s} = sX_j^Ty$ defined on $T =
J \times [ -1, 1 ]$. This stochastic process is simply a collection of
linear combinations of $y$, hence it is Gaussian under the assumption
of Gaussian errors. The \emph{Karush-Kuhn-Tuckher (KKT) conditions}
(ref???) imply that $\lambda_1 = \max_j |X_j^Ty|$. By introducing the
sign variable $s$, we can remove the absolute value and write
$\lambda_1$ as the maximum of our Gaussian process

\begin{equation}
\lambda_1 = \max_{(j,s)} f_{j,s}
\end{equation}

We have exhibited the first knot as the maximum of a Gaussian
process. We can do this for the second knot by introducing a new
process. Let $(j_1, s_1)$ be the maximizer so that $\lambda_1 =
s_1X_{j_1}^Ty$, and define 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{equation}
\begin{aligned}
  f^{(j_1,s_1)}_{(j,s)} & = \frac{ sX_j^T y - s X_j^T X_{j_1} X_{j_1}^Ty  } { 1 -  ss_1 X_j^TX_{j_1}} \\
  & = \frac{ sX_j^T(I-P_{j_1}) y }{ 1 -  s_1 X_{j_1}^T X_js}
\end{aligned}
\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
where $P_j$ is the projection onto the subspace spanned by $X_j$. We
can think of this as a ``residual process'' after regressing out the
maximum. Write $M = \max_{j \neq j_1, s} f^{(j_1,s_1)}_{(j,s)}$, the
maximum of this residual process. It can be shown from the KKT
conditions that $M  = \lambda_2$. To summarize, we have represented
the first two knots of the lasso solution path as the maxima of some
natural Gaussian processes. Distributional facts about Gaussian
processes now allow us to make conclusions about the distribution of
functions of the knots.

\subsection{Group lasso}
To extend this argument to the group lasso we need to define Gaussian
processes that characterize the knots of the group lasso solution
path.

\todo Either use the simplified argument in the case of equal weights
(equal group sizes), or finish adjusting the proof of $M = \lambda_2$
to include the weights and use that version. The proof can go in an
appendix.

\todo Modify write-up to match notation with \cite{tests:adaptive} and
then paste it in here

>>>>

\newcommand{\jonathan}[1]{{\color{blue}  #1}}

@@

Forward stepwise regression is a classical model selection procedure
that begins with an empty model and sequentially adds the best predictor
variable in each step. The usual $\chi^2$ and $F$-tests for significance
fail when a model has been selected this way and tend to be
anti-conservative unless they are computed on a held-out validation
dataset. In the lasso setting, \cite{significance:lasso} derived
a novel test statistic and its asymptotic null distribution, making
possible valid inferences after model selection using the full data.
\cite{tests:adaptive} modified and extended those results to the
group lasso \citep{grouplasso} and other penalized regression
problems, but only under the global null hypothesis.
One of the strengths of these test statistics is that they can be
used for valid significance testing when computed on the same
data used for model selection, eliminating the need for data splitting or for situations in which
data splitting is not appropriate.
The present work iteratively applies the global null test
of \cite{tests:adaptive} for each step in forward stepwise selection,
and works out some of the details necessary for
models with grouped variables. The resulting method can
be more statistically efficient than validation on held-out data, and
more computationally efficient than penalized methods with
regularization parameters chosen by cross-validation.

In Section~\ref{sec:stepwise} we establish notation and describe the
forward stepwise algorithm used in most of the paper.
Section~\ref{sec:testing}  reviews some recent work on
post-selection inference: \cite{significance:lasso,tests:adaptive,lasso:fixed}
relevant to our work here, and we describes a general framework
for post-selection inference based on quadratic comparisons.
Simulation results in Section~\ref{sec:simulations} show
empirically that our method performs well in settings where forward
stepwise itself performs well, and that
various stopping rules using our test statistic--including
some from \cite{sequential:fdr}--appear promising. In
Section~\ref{sec:applications} we apply
the method to several variants of forward
stepwise tailored to models with interactions and generalized additive
models, as well as to a real data example.
(\todo Change this paragraph if necessary as the sections are completed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Denote $y \in \real^n$ for $n$ i.i.d. measurements of the outcome variable.
Let an integer $G \geq 2$ be the number of groups of explanatory variables.
For each $1 \leq g \leq G$ the design matrix encoding the
$g$th group is the $n \times p_g$ matrix denoted $X_g$, where $p_g$ is
the number of individual variables or columns in group $g$.
% Do we need to assume $p_g \ll n$ or $\text{rank}(X_g) = p_g$?
When a group encodes a categorical variable as binary indicators for the
levels of that variable, by default we use the full encoding with a column for every
level. Although this introduces collinearity, our method does not require
the design matrix to have full rank.

Define $p = \sum_{g=1}^Gp_g$,
the total number of individual variables, so $p = G$ in the
case where all groups have size 1. Let $X$ be the matrix constructed
by column-binding the $X_g$, that is  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{equation*}
X = \begin{pmatrix} X_1 & X_2 & \cdots & X_G  \end{pmatrix}
\end{equation*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
For convenience, we assume throughout that the individual columns of $X$ are scaled to
have unit 2-norm (we do not scale groups, this is accomplished later
by weighting).
With each group we associate the $p_g \times 1$ coefficient vector
$\beta_g$, and write $\beta$ for the $p \times 1$ vector constructed
by stacking all of the $\beta_g$ in order.  Finally, our model for the
response is
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{equation}
\begin{aligned}
\label{eq:gmodel}
y | X& = X \beta + \sigma \epsilon \\
   & = \sum_{g=1}^G X_g \beta_g + \sigma \epsilon
\end{aligned}
\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
where $\epsilon$ is noise. We assume Gaussian noise
$\epsilon | X \sim N(0, \Sigma)$ with known covariance matrix $\Sigma$.

@@

\jonathan{Is $r_0=0$ or $y$? Should be defined in the algorithm. I also put a $y$ in below which I'm not sure
is correct or not. }

\begin{algorithm}
  \caption{Forward stepwise variant with groups and weights}
  \label{algo:fs}
  \begin{algorithmic}[1]
    \REQUIRE An $n$ vector $y$ and $n \times p$ matrix $X$ of $G$ variable groups with weights $w_g$
    \ENSURE Ordered active set $A$ of variable groups included in the model at each step
    \STATE $A \gets \emptyset$, $A^c \gets \{ 1, \ldots, G\}$
    \FOR{$s=1$ to $steps$}
    \STATE $g^* \gets \argmax_{g \in A^c} \{ \norm{X_g^T(y- r_{s-1})}_2 / w_g \}$
    \STATE $P_{g^*} \gets I_{n\times n} - X_{g^*}X_{g^*}^\dagger$
    \STATE $A \gets A \cup \{ g^* \}$, $A^c \gets A^c \backslash \{ g^* \}$
    \FORALL{$h \in A^c$}
      \STATE $X_h \gets P_{g^*} X_h$
    \ENDFOR
    \STATE $r_s \gets P_{g^*} r_{s-1}$
    \ENDFOR
    \RETURN $A$
  \end{algorithmic}
\end{algorithm}

The active set $A$ contains variable groups chosen to be included in
the model. Fitting $\hat \beta$ can be done by tracking the individual
fits and projections, or by simply fitting a linear model on the submatrix
of $X$ corresponding to $A$. 
We now use forward stepwise to refer specifically to
Algorithm~\ref{algo:fs} unless otherwise specified. Note that other
implementations of forward stepwise use different criteria for choosing
the next variable to add, such as the correlation with the residual.
Since we do not renormalize the columns after projecting the covariates
(lines 6 to 8 above), and since we have weights, we are generally not computing
correlations unless the design matrix is orthogonal and all weights are 1. We could
renormalize the columns, though we choose not to.
There are advantages and disadvantages to both criteria which we do not
discuss. Our choice was motivated by the group lasso result in
\cite{tests:adaptive}, but we believe other criteria can be handled
with appropriate modifications.

@@

Among model selection procedures, forward stepwise is one which performs
variable selection: from a potentially large set of variables it chooses
a subset to include in the model. The most general form of variable
selection is  "best-subset" selection, a procedure which searches among
all $2^G$ subsets of $G$ variable groups and picks the best model.
This exhaustive search is computationally infeasible when $G$ is
large, and when possible it still
runs the risk of over-fitting unless model complexity is
appropriately penalized (as in \eqref{eq:subsetregress} below).
Forward stepwise produces a much
smaller set of potential models, with cardinality at most
\textit{steps}. However
it is a greedy algorithm, so the set of models it produces may not
contain the best possible model. This is an inherent shortcoming of
forward stepwise procedures and should be kept in mind when choosing
between model selection methods.

@@

\jonathan{Is average power the same as TPR (or, more correctly, TPP)?}

For various sparsity levels $k$, Algorithm~\ref{algo:fs} was run on
various data sets with \textit{steps} equal to $k$ and the ``average
power'' was calculated as the number of true variables in the active
set after $k$ steps divided by $k$:
$$
\text{Power}_k = \frac{\# \left\{g: g \in A_k, \beta_g \neq 0\right\}}{k}.
$$ (\todo Make this consistent with
$\gamma$ in simulations section)
Nonzero coefficients had magnitude
in a range of multiples of $\gamma := \sqrt{2\log(G)}$, e.g. in $[1.4
\gamma, 1.6 \gamma]$. Results are shown in
Figure~\ref{fig:fwdstepsim}. After computing the
coherence of these design matrices, some calculations show the required
sparsity level to guarantee exact recovery in these situations is
about 2 or smaller, and the required nonzero coefficient magnitude is
likely in the range of 10 to 100 times $\gamma$. These simulations are far
from the stringent conditions required by theory to guarantee perfect
recovery, but the performance, while not perfect, may still be good
enough for some purposes.

@@

Writing $\hat \beta(\lambda)$ for the lasso solution for a fixed value of $\lambda$, we recall
the following facts summarized in \cite{significance:lasso,tibshirani_lasso_uniqueness}.

@@

  \item The vector valued function $\hat \beta(\lambda)$ is a
    continuous function of $\lambda$. For the lasso path, the
    coordinates of $\hat \beta(\lambda)$ are piecewise linear with
    changes in slope occurring at a finite number of $\lambda$ values
    referred to as \emph{knots}. 
    \item The knots depend on the data and are
    usually written in order $\lambda_1 \geq \lambda_2 \geq \cdots
    \geq \lambda_r \geq 0$.

@@

The covariance test (assuming $X$'s columns are of length one and $\Sigma = \sigma^2 I$ is at the
first step by
\begin{equation}
\label{eq:covtest}
T_1 = \frac{\lambda_1(\lambda_1-\lambda_2)}{\sigma^2} \overset{n,p \to \infty}{\to} \text{Exp}(1).
\end{equation}
In \cite{tests:adaptive} it is pointed out 
\begin{equation}
\label{test:exact}
\exp\left(- \frac{\lambda_1(\lambda_1-\lambda_2)}{\sigma^2} \right) \approx \frac{1 - \Phi(\lambda_1/\sigma)}{1 - \Phi(\lambda_2 / \sigma)} \overset{D}{=} \text{Unif}(0,1).
\end{equation}
Further, the above test statistic can be understood as the survival function of $\lambda_1 = \|X^Ty\|_{\infty}$
{\em conditional} on which variable achieves $\lambda_1$ as well as its sign.
The limiting results about later steps in \cite{significance:lasso} can (formally) be interpreted as
recursively applying $T_1$ to the variables that had not previously been selected by LARS.

In the setting of grouped variables, we use an analogous test statistic to
the right hand side of \cite{test:exact}. The test statistic is presented as an example
in \cite{tests:adaptive} though we re-derive it here in simpler form. The test draws inspiration
from the group LASSO.

@@

There is a largest value of $\lambda$ such that $\hat{\beta}_{\lambda}=0$ which corresponds to $\lambda_1$
in the LASSO setting:
\begin{equation}
\label{eq:lammax}
\lambda_1^{\text{group}} = \max_{g} \frac{1}{w_g}\|X_g^Ty\|_2 . 
\end{equation}
Formally, the value above is just the dual norm of the penalty
$$
{\cal P}(\beta) = \sum_{g=1}^G w_g \| \beta_g \|_2
$$
hence it can be expressed as
\begin{equation}
\label{eq:lammax}
\lambda_1^{\text{group}} = \max_{g} \frac{1}{w_g}\|X_g^Ty\|_2 = \frac{1}{w_{g^*}}\eta_{g^*}^TX_{g^*}^Ty . 
\end{equation}
where $g^*$ is the group that achieves the max and 
$\eta_{g^*} = X_{g^*}^Ty / \|X_{g^*}^Ty\|_2$ is the $\ell_2$ unit vector that achieves $\|X_{g^*}^Ty\|_2$.

@@

\begin{figure}
\begin{center}
\resizebox{!}{3in}{\input{curved.pdf_tex}}
\end{center}
Selection conditioned on an arbitrary selection event.
\end{figure}
We are interested in inference after a selection procedure, say, $S$, for
which the selection event is the intersection of a list of quadratic inequalities:

$$
\begin{aligned}
\{S(y)=s\} = \cap_{i \in I(s)} \{y: y^TQ_iy + a_i^Ty\leq b_i \}.
\end{aligned}
$$

The quadratic forms are not assumed non-negative definite, but we can, without loss of generality
assume they are symmetric.

If we consider forward stepwise with groups the selection procedure is just
choosing the first group, $g^*$ and we have
$$
\{g^*(y)=g\} =  \cap_{h \neq g} \{y: y^T(X_hX_h^T/w_h^2 - X_gX_g^T/w_g^2)y \leq 0\}.
$$

We want to slice through the selection event along a ray with direction $\eta$ that passes through $y$. 
That is, we need to find
$$
\begin{aligned}
\left\{t: S(y+t\eta)=s \right\} &= \cap_{i \in I(s)} \left\{t: (y+t\eta)^T Q_i (y+t\eta) + a_i^T(y+t\eta) \leq b_i\right\}. \\
\end{aligned}
$$

For any given $i \in I(s)$ we see that
$$
\begin{aligned}
\left\{t: (y+t\eta)^T Q_i (y+t\eta) + a_i^T(y+t\eta) \leq b_i\right\} &= \left\{t: t^2 \cdot \eta^TQ_i\eta + t \cdot(2 y^TQ_i\eta + a_i^T\eta) + y^TQ_iy + a_i^Ty - b_i \leq 0 \right\} \\
&= \text{Intervals}(Q_i,a_i,b_i,y,\eta)
\end{aligned}
$$

Each value of $\text{Intervals}(Q_i,a_i,b_i,y,\eta)$ above is one of:
- $\emptyset$, in which case the selection event is also the $\emptyset$ (so this never occurs);
- $(-\infty, L(Q_i,a_i,b_i,y,\eta)] \cap [U(Q_i,a_i,b_i,y,\eta), \infty)$ if $\eta^TQ_i\eta < 0$;
- $[L(Q_i,a_i,b_i,y,\eta), U(Q_i,a_i,b_i,y,\eta)]$ if $\eta^TQ_i\eta > 0$;
- $(-\infty, L(Q_i,a_i,b_i,y,\eta)]$ if $\eta^TQ_i\eta=0$ and $2 y^TQ_i\eta + a_i^T\eta > 0$;
- $[U(Q_i,a_i,b_i,y,\eta), \infty)$ if $\eta^TQ_i\eta=0$ and $2 y^TQ_i\eta + a_i^T\eta < 0$;
- $(-\infty,\infty)$ if $\eta^TQ_i\eta=0, 2 y^TQ_i\eta + a_i^T\eta = 0$ and $y^TQ_iy + a_i^Ty - b_i \leq 0$.
